\papertitle

### 2012-10-13 manuscript.tex
Conclusion draft.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
We have demonstrated cooperative guidance of a 13 gram flapping wing MAV with a
lightweight base station in hardware. In addition, we produced a model of the
overall system by modeling the individual system capabilities, and composing
it with known system interactions. The corroboration between our simulated and
experimental results suggests that our simplified modeling approach may be useful for 
predicting the performance of collaborative systems.

We intend to further explore the benefits and limitations of collaboration in
unstructured environments by deploying our base station on millirobotic ground
platforms. As the base station used in this work was designed with this avenue
in mind, this is a matter of implementation. The effectiveness of our modeling
approach when applied to systems with more interactions and agents is also
a future area of interest.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
The authors would like to thank Fernando Garcia Bermudez for his 
assistance with the Vicon motion capture system, Andrew Pullin for his 
help with robot photography, and the members of the Biomimetic 
Millisystems Laboratory and the EECS community at the University of 
California, Berkeley for their advice and support.
